---
output:
  html_document:
    self_contained: no
    theme: cosmo
---
# JSM analysis
*Author: Matthew Shane Loop*

*Purpose: Summarize the results of the type 1 error rate simulation for the $K$ test, using only the conditions for the 2014 JSM presentation. Estimate the overall empirical type 1 error rate, and make a plot of the error rates at each range.*

## Load packages and data
```{r packages}
library(dplyr)
library(ggplot2)
```

```{r data}
jsm <- read.table(file = "results.txt", sep = "\t", header = TRUE)
jsm <- tbl_df(jsm)
jsm
```

## Overall type 1 error rate
The observed type 1 error rates for each condition are
```{r overall-rate,dpi=300,out.height='600px',out.width='1000px',fig.align='center'}
jsm_t <- group_by(jsm, tests)
alpha_hat_t <- (summarise(jsm_t,
                        n = n(),
                       alpha = mean(reject)
                       ))
alpha_hat_t <- mutate(alpha_hat_t,
       ci_low = alpha - 1.96*sqrt(alpha*(1-alpha)/n),
       ci_high = alpha + 1.96*sqrt(alpha*(1-alpha)/n))
alpha_hat_t
p <- ggplot(alpha_hat_t, aes(x = tests, y = alpha)) +
    geom_point() +
    geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5) +
    ggtitle("Empirical type 1 error rate vs. number of tests done") +
    ylab(expression(hat(alpha))) +
    theme_bw(base_size = 48, base_family = "") +
    geom_hline(yintercept = 0.05, lty = 2) +
    theme_bw() +
    ylim(ymin = 0.04, ymax = 0.06) +
    xlab("Number of tests")
p
```

## Type 1 error rate at each range
Now, let's take a look at the type 1 error rates per range tested.
```{r rate-by-range,warning=FALSE,message=FALSE,dpi=300,out.width='900px',out.height='1000px',fig.align='center'}
jsm_h <- group_by(jsm, tests, h)
jsm_h$tests <- as.factor(jsm_h$tests)
alpha_hat_h <- (summarise(jsm_h,
                        n = n(),
                       alpha = mean(reject)
                       ))
alpha_hat_h <- mutate(alpha_hat_h,
       ci_low = alpha - 1.96*sqrt(alpha*(1-alpha)/n),
       ci_high = alpha + 1.96*sqrt(alpha*(1-alpha)/n))

p <- ggplot(alpha_hat_h, aes(x = h, y = alpha, label = tests)) +
    geom_point() +
    geom_errorbar(aes(ymin = ci_low, ymax = ci_high)) +
    ggtitle("Empirical type 1 error rate vs. range, by number of tests done") +
    ylab(expression(hat(alpha))) +
    theme_bw(base_size = 48, base_family = "") +
    geom_hline(yintercept = 0.05, lty = 2) +
    theme_bw() +
    ylim(ymin = 0, ymax = 0.1) +
    xlab("Range (miles)")
p +facet_grid(tests ~ .)
```